AbxD01 Analysis

### 2015-01-30 Figure 6/abxD01.optimizingModel.Rmd
fix graphs, model

``` {r, eval=TRUE}
#################################
###rf of the delay data
delay<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.delay.regression.logtrans.filter16mintot.csv", header=T)
delay<-delay[,-1]

>>>>

``` {r, eval=TRUE}
#################################
###rf of the delay data
delay<-read.csv("~/Desktop/mothur/abxD01/rf/abxD01.final.an.unique_list.0.03.subsample.0.03.pick.shared.rf.delay.regression.logtrans.filter16mintot.noUntr.csv", header=T)
delay<-delay[,-1]

### 2015-01-30 abxD01_analysis.Rmd
fix graphs, model

>>>>

Statistical comparison of delayed and on time CFU results:
```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.allmetro.forlogscale.fig5.csv", header=T)
file<-file[file$expgroup!="1untr",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
metro_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p < 0.0001
#strep_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# all significantly different
metro.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(metr.aov)
#TukeyHSD(strep.aov)
metro_ttest <- t.test(file$nextDayCFU~file$expgroup)
# both significantly different
```
